Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-16 writeup/gz_hubble_data.tex
added specz flag to dropbox metadata tables and explanation text in sec 2.5
Edits from @bamford on image creation.

The images used for classification in GZH were color-composite JPGs made from
multi-band data. The exact process for creating the images depended on the bands
and resolutions in the surveys.

For galaxies in the ACS-GC, color composites were made using a fixed pixel
intensity scaling with weights of
$[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue
channels respectively. A nonlinear mapping was applied to each pixel to
emphasize the contrast in faint features \citep{lup04}, taking the form of:

\begin{equation}
I_\mathrm{channel,new} = I_\mathrm{channel,old} \times \frac{\arcsinh(b\times r)}{(b\times r)}
\label{eqn:nonlinear}
\end{equation}

\noindent GZH images from \citet{gri12} used a value of $b=3$.

The majority of the data in Legacy surveys described in
Section~\ref{ssec:legacy_surveys} had images in only one or two filters
available when the GZH project was first launched, making standard 3-channel
RGB images in the same method used for the SDSS images in the original Galaxy
Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the
two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the
blue channel, the higher-wavelength band to the red channel, and the green
channel created by taking the geometric mean of the two. Bands used in each of
the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and
GOODS-S images used different filters --- this was a deliberate choice made so
that the GEMS images could be directly compared with the overlapping coverage
of GOODS-S (Figure~\ref{fig:filtercurves}).

By the time that the 5-epoch sets of GOODS data were put into GZH (in March
2015), coverage in four separate \hst{} bands were publicly available. The
deeper GOODS images were created using the arithmetic mean of \Bband{} and
\Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the
green channel. These images also had their speckled noise pixels decolorized.

The COSMOS images only had the \Iband{} imaging available at the time of
classification in GZH. For these galaxies, GZH used ``pseudocolor'' images
created by using the ACS \Iband{} data as an illumination map and ground-based
imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to
provide the color gradients \citep[see][for further details]{gri12}. This
resulted in images with the angular resolution of \hst{}
($\sim0.05$~\arcsec/pixel) for the overall intensity, but color gradients at
ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{}
\citep{tan07}.

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and made into color composites using the method of \citet{lup04}.

To deal with situations in which the sky noise was highly colored (which might
have been a distraction to visual classification), a soft-edged object mask was
applied to the coadded Stripe~82 and the COSMOS images. This mask preserved the
color balance for galaxies, but desaturated speckled noise against regions of
blank sky.

>>>>

The images used for classification in GZH were color-composite JPEGs made from
multi-band data. These were created followed the method of \citet{lup04}, which
preserves colour information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centers. The relative scalings of the filter bands were
chosen while trying to reproduce the color appearance of the SDSS images in
previous iterations of Galaxy Zoo.

Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
provided images in only two filters. For these, the shorter-wavelength band was
mapped to the blue channel, the longer-wavelength band to the red channel, and
the green channel created by taking the arithmetic mean of the two. The bands
used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
Although four bands were available for the GOODS survey, only two bands were
used to create the original 2-epoch images, for consistency with AEGIS and
GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
filters --- this was a deliberate choice made so that the GEMS images could be
directly compared with the overlapping coverage of GOODS-S
(Figure~\ref{fig:filtercurves}).

Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
GOODS images were added into GZH later (in March 2015). These images made
use of the full four-band data by using the arithmetic mean of \Bband{} and
\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
the red channel.

The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
launch.  These galaxies used ``pseudocolor'' images created by using
the ACS \Iband{} data as an illumination map and ground-based imaging from the
\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
information (see \citealt{gri12} for further details). This resulted in images
with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
overall intensity, but color gradients at ground-based resolution, with seeing
between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in a corresponding manner.

In some cases, we found that attempting to emphasize faint features in the
images resulted in the sky noise taking the appearance of brightly colored
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the color images and a desaturation operation performed.
This masked procedure was effective in preserving the color balance for
galaxies, retaining the visibility of faint features, but reduced the color
contrast in the sky noise and greatly improved the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.
